---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# armgin

The armgin package summarises all combinations of grouping variables at once.
For example, vote counts by

```
* voting place, ward, constituency, party, candidate
* voting place, ward, constituency, party
* voting place, ward, constituency
* voting place, ward,
* voting place
```

Or with `hierarchy = FALSE` and grouping by only voting place, ward and
constituency (for brevity)

```
* voting place, ward, constituency

* voting place, ward
* voting place, constituency
* ward, constituency

* voting place
* ward
* constituency
```

Groups are defined as normal by `dplyr::group_by()` and then piped into
`margins()`

```{r}
mtcars %>%
  group_by(cyl, gear, am) %>%
  margins(mpg = mean(mpg),
          hp = min(hp)) %>%
  print(n = Inf)
```

## Installation

You can install the development version from GitHub with devtools or remotes.

```r
install.packages("devtools")
devtools::install_github("nacnudus/armgin")
```

Please note that the 'armgin' project is released with a [Contributor Code of
Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree
to abide by its terms.
